Lattice Boltzmann study of mass transfer for complicated geometries

### 2011-11-10 Text/introduction.tex
Added cylinder benchmark.
A second benchmark.

Here some

>>>>

The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. Some examples for
different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/cylinder1666.eps}
\includegraphics[width=0.5\textwidth]{Figures/cylinder0833.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/cylinder0104.eps}
\includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
\caption{Profiles for different diffusion parameters. One can see that the diffusion is captured
accurately in non-dimensional space \label{fig:cylinder:benchmark}.}
\end{figure}

\subsection{Steady mass transfer}
The problem we want to address can be formulated through the following PDE:
\beq
\begin{aligned}
&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
&C(0,y)=0,\, C(x,0)=C_s,\, \frac{\partial C}{\partial_y }(x,\delta)=0\\
&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
\end{aligned}
\feq
